Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
DSN changes

We note that while these collisions are state independent and include
multicollisions, none of these attacks are always multicollisions. Many of the
blocks we've found only collide under the initial state value. Because of this,
these collisions are only useful if you know the current state where a
colliding pair is to be injected. Thus, this is one area in which collisions
could potentially improve.

@@

\subsection{Recapitulation}

@@

Through the exploration of the neighborhood technique, we have found over
35,000 new differential paths which originated from the five original
collisions in MD4. This shows that the neighborhood definition is sufficient
to produce a large quantity of new collision classes. Further, we give
evidence for propagating neighborhoods across reduced round versions of MD4.

@@

Even under successive unit neighborhoods, the family of input block
differentials remains roughly the same among successive neighborhoods,
echoing the work of M. Schl{\"a}ffer and E. Oswald \cite{Schlaffer2006}.
This can be partially counteracted by moving to reduced-round spaces,
evaluating the neighborhood, and expanding back to a collision in
full-round MD4. That is, there is a detectable signature of sharing
significant input block differential structure with the original
collision. Our 35,918 collision classes belonged to 176 unique
families of collisions. However, there were only three unique families
of input block differentials with 100 input block differences. Note
however, that the unlike the metric evaluations in
Section \ref{empirical:differentials}, these collision classes were
not evaluated for number of unique differentials; thus there are likely
more than 100 patterns, but still only three families.

@@

Further, compared to the work presented by M. Schl{\"a}ffer and E. Oswald
\cite{Schlaffer2006}, this is a 35 fold increase. Increasing this bound is
possible with low additional cost. Further, by fully considering the
similarities of collision families under $\precsim$ and better enumerating the
resulting candidates, additional paths with unique differentials could be
constructed. This would allow for new candidate input block differentials,
better construction of chosen prefix attacks, and potentially to a full second
preimage attack without relying on message modification techniques.

>>>>

We note that while these collisions are state independent and include
multicollisions, none of these attacks are always multicollisions. Many of the
blocks we've found only collide under the initial state value. Because of this,
strict multicollision attacks are only useful if you know the current state where a
colliding pair is to be injected. Thus, this is one area in which collisions
could potentially improve.

@@

@@

Through the exploration of the neighborhood technique, we have found over
35,000 new differential paths which originated from the five original published
collisions in MD4. This shows that the neighborhood definition is sufficient
to produce a large quantity of new collision classes. Further, we give
evidence for propagating neighborhoods across reduced round versions of MD4.

@@

Even under successive unit neighborhoods, the family of input block
differentials remains roughly the same among successive neighborhoods,
echoing the work of M. Schl{\"a}ffer and E. Oswald \cite{Schlaffer2006}.
This can be partially counteracted by moving to reduced-round spaces,
evaluating the neighborhood, and expanding back to a collision in
full-round MD4. That is, there is a detectable signature of sharing
significant input block differential structure with the original
collision. Our 35,918 collision classes belonged to 176 unique
families of collisions. However, there were only three unique families
of input block differentials with 100 input block differences. Note
however, that unlike the metric evaluations in
Section \ref{empirical:differentials}, these collision classes were
not evaluated for number of unique differentials; thus there are likely
more than 100 patterns, but still only three families.

@@

Further, compared to the work presented by M. Schl{\"a}ffer and E. Oswald
\cite{Schlaffer2006}, this is a 35 fold increase. Increasing this yield is
possible with low additional cost. Further, by fully considering the
similarities of collision families under $\precsim$ and better enumerating the
resulting candidates, additional paths with unique differentials could be
constructed. This would allow for new candidate input block differentials,
better construction of chosen prefix attacks, and could potentially lead to a full second
preimage attack without relying on message modification techniques.
